Roster Review (Generic)

### 2019-07-25 rosterReview_generic.Rmd
minor adjustments to generic roster review and latest lineups

@@

```{r trade_eval}
# TODO find way to wrap these three views into one
rosters %>% 
  filter(grepl("Plouffe|Mata",team)) %>% 
  select(team, manager, name_full, display_position, zar, positions) %>% 
  arrange(zar %>% desc) %>% 
  mutate(zar = zar %>% round(1)) %>% 
  View("Trade Partner")
  # mutate(zar = janitor::round_half_up(zar)) %>% 
  # write_csv("data/tradeReview_20190423.csv")

rosters %>% 
  filter(grepl("Plouffe|Mata",team)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type)), width=.2) +
  coord_flip() -> tv

>>>>

```{r myteam}
rosters %>% 
  filter(grepl("Plouffe",team)) %>% 
  select(name_full, positions, zar) %>% 
  arrange(zar %>% desc) %>% 
  View("My Team")
```

@@

```{r trade_eval}
# TODO find way to wrap these three views into one
rosters_by_position %>% 
  filter(grepl("Plouffe|Bumpin",team)) %>% 
  select(team, manager, name_full, display_position, zar, pos_zar, positions, draft_round) %>% 
  arrange(zar %>% desc) %>% 
  mutate(zar = zar %>% round(1)) %>% 
  View("Trade Partner")
  # mutate(zar = janitor::round_half_up(zar)) %>% 
  # write_csv("data/tradeReview_20190423.csv")

rosters %>% 
  filter(grepl("Plouffe|Bumpin",team)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type)), width=.2) +
  coord_flip() -> tv
